Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults

### 2023-03-16 ribose-paper.RMD
discussion updates

Interestingly, we did observe a linear relationship between total RNA and UBF, supporting the observations from diabetic mice in Mariappan et al. (2011). This was not evident with total RNA and c-Myc or rpS6, which we observed no linear relationship between. The upstream binding factor (UBF) has indeed previously been described as a master regulator of rDNA transcription, based on findings from cell cultures [@figueiredo_regulation_2019; @kusnadi_regulation_2015; @russell_rna-polymerase-i-directed_2005]. However, it has only recently been found in a linear relationship with total RNA content in human skeletal muscle cells after a short period of RT [@hammarstrom_ribosome_2022]. As such, UBF also seem to respond to mechanical loading in human muscle cells in line with responses seen in cell cultures and synergist ablation models [@mariappan_ribosomal_2011; @von_walden_mechanical_2012], in addition to the previously reported response to hormonal, nutritional, and cellular energy signals [@figueiredo_regulation_2019; @kusnadi_regulation_2015; @russell_rna-polymerase-i-directed_2005]. Regarding c-Myc, it has previously been found to regulate gene chromatin remodelling and Pol I availability in non-muscle cells [@poortinga], and c-Myc overexpression stimulated skeletal muscle ribosome biogenesis in mice [@mori], similar to the rapamycin-independent upregulation after RT in rats [@west]. However, the findings of the present study do not entirely align with these previous observations, as there was no difference in change of total RNA and rRNA between treatments, despite a significantly greater c-Myc content in placebo compared to glucose post intervention. Along with the observed non-linear relationship between c-Myc and total RNA, while important as a general transcription factor, c-Myc does not seem to have the same specificity to stimulate rDNA transcription as UBF, in human skeletal muscle cells. Further, the ribosomal protein S6 (rpS6) has previously been shown to correlate strongly with rRNA content after synergist ablation [@nakada_correlation_2016; @chaillou_hypoxia_2012], and is suggested as a reliable measurement of ribosome biogenesis [@nakada_correlation_2016]. Together, this may explain why the between treatment difference in c-Myc content did not induce differences in total RNA or rRNA content, as the specific transcription factor UBF and the rpS6 increased equally with both treatments. Notably, the difference between c-Myc in glucose and placebo may have stimulated pathways not measured in the present study.

>>>>

Interestingly, we did observe a linear relationship between total RNA and UBF, supporting the observations from diabetic mice in Mariappan et al. (2011). This was not evident with total RNA and c-Myc or rpS6, which we observed no linear relationship between. The upstream binding factor (UBF) has indeed previously been described as a master regulator of rDNA transcription, based on findings from cell cultures [@figueiredo_regulation_2019; @kusnadi_regulation_2015; @russell_rna-polymerase-i-directed_2005]. However, it has only recently been found in a linear relationship with total RNA content in human skeletal muscle cells after a short period of RT [@hammarstrom_ribosome_2022]. As such, UBF also seem to respond to mechanical loading in human muscle cells in line with responses seen in cell cultures and synergist ablation models [@mariappan_ribosomal_2011; @von_walden_mechanical_2012], in addition to the previously reported response to hormonal, nutritional, and cellular energy signals [@figueiredo_regulation_2019; @kusnadi_regulation_2015; @russell_rna-polymerase-i-directed_2005]. Regarding c-Myc, it has previously been found to regulate gene chromatin remodelling and Pol I availability in non-muscle cells [@poortinga_c-myc_2011], and c-Myc overexpression stimulated skeletal muscle ribosome biogenesis in mice [@mori_c-myc_2021], similar to the rapamycin-independent upregulation after RT in rats [@west_acute_2016]. However, the findings of the present study do not entirely align with these previous observations, as there was no difference in change of total RNA and rRNA between treatments, despite a significantly greater c-Myc content in placebo compared to glucose post intervention. Along with the observed non-linear relationship between c-Myc and total RNA, while important as a general transcription factor, c-Myc does not seem to have the same specificity to stimulate rDNA transcription as UBF, in human skeletal muscle cells. Further, the ribosomal protein S6 (rpS6) has previously been shown to correlate strongly with rRNA content after synergist ablation [@nakada_correlation_2016; @chaillou_hypoxia_2012], and is suggested as a reliable measurement of ribosome biogenesis [@nakada_correlation_2016]. Together, this may explain why the between treatment difference in c-Myc content did not induce differences in total RNA or rRNA content, as the specific transcription factor UBF and the rpS6 increased equally with both treatments. Notably, the difference between c-Myc in glucose and placebo may have stimulated pathways not measured in the present study.
